Modeling the Evolution of Mimicry

### 2016-02-26 docs/paper/Paper.tex
10 pages!! Finally

\begin{table}[h!]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
		Hopfield Maximum Iterations & 20 & Maximum number of iterations to recognize a pattern and to avoid infinite loop in case the network never reaches a steady state. \\ \hline
		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
	\hline
\end{tabular}
\caption{Parameters to control predator population and pattern recognition capability.}
\label{tab:predator-control-parameters}
\end{table}

This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \citep{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \citep{holland1996} are present in this model. Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}. Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them. We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome. The model has its \textit{flow} as it progresses in time. Also there is \textit{diversity} of prey species in the environment.

@@

% Put the image
\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.7\textwidth]{../tex/images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.7\textwidth]{../tex/images/simTime8k-4Prey-unp}
	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure*}

>>>>

\begin{table}[h]
\small
\centering
\begin{tabular}{| l | c |}
	\hline
		\textbf{Parameter} & \textbf{Value} \\ \hline
		Minimum Memory Size & 2 to 6 \\ \hline
		Maximum Memory Size & 10 \\ \hline 
		Hopfield Maximum Iterations & 20 \\ \hline
		Attack Age & 500 \\ \hline
		Attack Interval & 100 \\ \hline
		Genome Mutation rate & 0.3 \\ \hline
		Reproduction Age Limit & 500 \\ \hline
		Reproduction Interval & 1000 to 3000 \\ \hline
		Demise Age & 2000 to 7000 \\
	\hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
\label{tab:predator-genome}
\end{table}

This model has been designed to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \citep{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \citep{holland1996} are present in this model. Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}. Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them. We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome. The model has its \textit{flow} as it progresses in time. Also there is \textit{diversity} of prey species in the environment.

@@

% Put the image
\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.75\textwidth]{../tex/images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure*}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.75\textwidth]{../tex/images/simTime8k-4Prey-unp}
	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure*}
